\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-01-21 manuscript/manuscript.tex
Tried Different Durations

\jy{Need a better opening sentence. Notation $\hat\theta_n$ and $F_n$ have
  not been defined.}

Let
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the
goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta)|.
\end{equation*}
where $F_n$ denotes the empirical distribution function based on $X_1,...,X_n$,
and $\hat\theta_n$ denotes the fitted parameters for the hypothesized 
distribution fitted onto $X_t$.
We note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x)),
\end{equation*}
where $F(x)$ is the true cdf (under the null $F(x) = F(x, \theta_0)$ for some
true parameter $\theta_0$).

@@

\jy{Not good opening sentence}
Let $E^{(b)}$ refer to the expectation with respect to
the bootstrap distribution. In this case, we can 
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$
\jy{The second term: does it depend on $b$? }
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x))$,
and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$ to
approximate $\sqrt{n}(F(x; \theta_n) - F(x))$'s distribution.

@@

\jy{How many replicates were used to estimate the size and power?}

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma.
For each setting for $F$, $\phi$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.

@@

Like we did to see if the test holds its size, we generated time series with 
marginal distributions $N(8, 8)$ and 
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. However, 
to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is gamma. Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0.
When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is normal.
For each setting for $F$, $\phi$, and $n$, we replicate the method $R$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, R\}$.

Given some significance level $\alpha$, we can compute a rejection rate 
$q = \#\{p_r < \alpha\} / R$ for $r \in \{1, \ldots, R\}$.
Additionally, we can construct a 95\% confidence interval for 
this rate. Below are tables containing rejection rates showcasing the 
differences when simulation settings are changed.

>>>>

First, let us consider how the KS statistic is typically computed for a sample
with no dependence structure.
Let $\hat\theta_n$ denote the fitted parameters for the hypothesized 
distribution fitted onto $X_t$, and let 
$F_n$ denote the empirical distribution function based on $X_1,...,X_n$
\jy{Need a better opening sentence. Notation $\hat\theta_n$ and $F_n$ have
  not been defined.}
\mc{addressed}

Let
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n)).
\end{equation*}
Then, the
goodness of fit statistic is 
\begin{equation*}
T_n := \sup_x|Y_n(x; \hat\theta)|.
\end{equation*}

We note that
\begin{equation*}
Y_n(x; \hat\theta) = \sqrt{n}(F_n(x) - F(x)) - 
\sqrt{n}(F(x; \hat\theta_n) - F(x)),
\end{equation*}
where $F(x)$ is the true cdf (under the null $F(x) = F(x, \theta_0)$ for some
true parameter $\theta_0$).

@@

We then use the bootstrap distribution to construct an approximation of
the KS statistic.
\jy{Not good opening sentence}\mc{addressed}
Let $E^{(b)}$ refer to the expectation with respect to
the bootstrap distribution. In this case, we can 
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$
\jy{The second term: does it depend on $b$? }
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x))$,
and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$ to
approximate $\sqrt{n}(F(x; \theta_n) - F(x))$'s distribution.

@@

\jy{How many replicates were used to estimate the size and power?}
\mc{addressed}

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\phi$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.

@@

Like we did to see if the test holds its size, we generated time series with 
marginal distributions $N(8, 8)$ and 
$\Gamma(8, 1)$, lag-1 autocorrelation $\phi \in \{-.4, -.2, 0, .2, .4\}$, and
sample size $n \in \{100, 200, 400, 600, 800, 1600, 3200\}$. However, 
to evaluate the test's power, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is gamma. Because the support of $N(8, 8)$ is
$(-\infty, \infty)$, but the support of $\Gamma(8, 1)$ is $(0, \infty)$, we used
the \textsl{truncdist} package \citep{truncdist} to truncate the series at 
values less than or equal to 0.
When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is normal. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\phi$, and $n$, we replicate the method $1000$ times 
to obtain a p-value $p_r$ for each $r \in \{1, \ldots, 1000\}$.

Given some significance level $\alpha$, we can compute a rejection rate 
$q = \#\{p_r < \alpha\} / 1000$ for $r \in \{1, \ldots, 1000\}$.
Additionally, we can construct a 95\% confidence interval for 
this rate. Below are tables containing rejection rates showcasing the 
differences when simulation settings are changed.
